---
title: "Fig2 and fig3"
author: "Jens Petersen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
fig_width: 3
fig_height: 2
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE,fig.path = 'Figs/')
```


```{r echo=FALSE, message=FALSE}
grDevices::pdf.options(useDingbats = FALSE)
knitr::opts_chunk$set(fig.width=3, fig.height=2) 
library(dplyr)
library(ggplot2)
library(drc)
library(forcats)
library(ggsignif)
```



## This script runs a summary of all petri dish spot assays.


```{r}
BindingAssays=read.csv("Data/Fig2and3BindingAssays.csv")
```

Each row represents the date which the parasites were purified and added to the petri dish. Each experiment was performed in duplicate petri dishes with mixed hemoglobin genotypes on each of petri dish. Each petri dish contained 16 protein spots. 3 images was taken at 10x for each protein spot.

Normalized to binding at 10µg/ml being max with CD36 for 3d7 and IT4var30 and EPCR for IT4var20.

Wilcoxon tests:
```{r}
wilcox.test(BindingAssays$Count[BindingAssays$Parasite=="3d7"&BindingAssays$Concentration==10&BindingAssays$Receptor=="CD36"&BindingAssays$Genotype=="AS"],BindingAssays$Count[BindingAssays$Parasite=="3d7"&BindingAssays$Concentration=="10"&BindingAssays$Receptor=="CD36"&BindingAssays$Genotype=="AA"],paired=T)

wilcox.test(BindingAssays$Count[BindingAssays$Parasite=="IT4var30"&BindingAssays$Concentration==10&BindingAssays$Receptor=="CD36"&BindingAssays$Genotype=="AS"],BindingAssays$Count[BindingAssays$Parasite=="IT4var30"&BindingAssays$Concentration=="10"&BindingAssays$Receptor=="CD36"&BindingAssays$Genotype=="AA"],paired=T)

wilcox.test(BindingAssays$Count[BindingAssays$Parasite=="IT4var20"&BindingAssays$Concentration==10&BindingAssays$Receptor=="EPCR"&BindingAssays$Genotype=="AS"],BindingAssays$Count[BindingAssays$Parasite=="IT4var20"&BindingAssays$Concentration=="10"&BindingAssays$Receptor=="EPCR"&BindingAssays$Genotype=="AA"],paired=T)
```

```{r, echo=F,warning=F,message=F, fig.width=1.6, fig.height=2, useDingbats=FALSE}
p1<-ggplot(subset(BindingAssays,BindingAssays$Concentration==10&BindingAssays$Parasite=="3d7"),aes(x=Receptor,y=Count,fill=Genotype,alpha=0.9))+
  geom_boxplot()+
 geom_jitter(aes(color=Genotype), position = position_jitterdodge())+theme_bw()+ylab("Cells per image")+
  scale_alpha(guide=F)+
  scale_fill_manual(values=c("#C84E00", "#339898"),guide=guide_legend(override.aes = list(alpha = 0.6)))+
  scale_color_manual(values=c("#C84E00", "#339898"),guide=guide_legend(override.aes = list(alpha = 0.6)))+
   theme(legend.title=element_blank(),legend.justification = c(1, 1), legend.position = c(0.98,0.98),legend.background = element_rect(),legend.key.size = unit(0.05, "inch"),legend.key.width=unit(0.1, "inch"))+
  coord_cartesian(ylim=c(0,3000))

s <- data.frame(stringsAsFactors=FALSE,
                             p.adj = 0.0001,signif = "AA CD36 - AS CD36",y_position = c(3000),xmin = c(0.8),xmax = c(1.2),Genotype = as.factor(c("AA", "AS")))
```


```{r, echo=F,warning=F,message=F, fig.width=3, fig.height=4, useDingbats=FALSE}
p2<-ggplot(subset(BindingAssays,BindingAssays$Concentration==10&BindingAssays$Parasite=="IT4var30"),aes(x=Receptor,y=Count,fill=Genotype,alpha=0.9))+geom_boxplot()+geom_jitter(aes(color=Genotype), position = position_jitterdodge())+theme_bw()+ylab("Cells per image")+
  scale_alpha(guide=F)+scale_shape_manual(values = c(16))+
  scale_fill_manual(values=c("#C84E00", "#339898"),guide=guide_legend(override.aes = list(alpha = 0.6)))+
  scale_color_manual(values=c("#C84E00", "#339898"),guide=guide_legend(override.aes = list(alpha = 0.6)))+
   theme(legend.title=element_blank(),legend.justification = c(1, 1), legend.position = c(0.98,0.98),legend.background = element_rect(),legend.key.size = unit(0.05, "inch"),legend.key.width=unit(0.1, "inch"))+
  coord_cartesian(ylim=c(0,3000))

s30 <- data.frame(stringsAsFactors=FALSE,
                             p.adj = 0.03,signif = "AA CD36 - AS CD36",y_position = c(2800),xmin = c(0.8),xmax = c(1.2),Genotype = as.factor(c("AA", "AS")))
```

```{r, echo=F,warning=F,message=F, fig.width=1.6, fig.height=2, useDingbats=FALSE}
p3<-ggplot(subset(BindingAssays,BindingAssays$Concentration==10&BindingAssays$Parasite=="IT4var20"),aes(x=fct_rev(as.factor(Receptor)),y=Count,fill=Genotype,alpha=0.9))+geom_boxplot()+geom_jitter(aes(color=Genotype), position = position_jitterdodge())+theme_bw()+ylab("Cells per image")+xlab("Receptor")+
  scale_alpha(guide=F)+
  scale_fill_manual(values=c("#C84E00", "#339898"),guide=guide_legend(override.aes = list(alpha = 0.6)))+
   scale_color_manual(values=c("#C84E00", "#339898"),guide=guide_legend(override.aes = list(alpha = 0.6)))+
   theme(legend.title=element_blank(),legend.justification = c(1, 1), legend.position = c(0.98,0.98),legend.background = element_rect(),legend.key.size = unit(0.05, "inch"),legend.key.width=unit(0.1, "inch"))+coord_cartesian(ylim=c(0,5000))

s20 <- data.frame(stringsAsFactors=FALSE,
                             p.adj = c(0.0002),signif = "AA EPCR - AS EPCR",y_position = c(5000),xmin = c(0.8),xmax = c(1.2),Genotype =c("AA", "AS"))
```

```{r, echo=F,warning=F,message=F, fig.width=1.6, fig.height=2, useDingbats=FALSE}
p1+ geom_signif(
    aes(xmin = 0.8, xmax = 1.2, y_position = 2500, annotations = "***"),data = s, manual = TRUE, tip_length = 0.01)

p2+ geom_signif(
    aes(xmin = 0.8, xmax = 1.2, y_position = 2800, annotations = "*"),data = s30, manual = TRUE, tip_length = 0.01)

p3+ geom_signif(
    aes(xmin = 0.8, xmax = 1.2, y_position = 4600, annotations = "**"),data = s20, manual = TRUE, tip_length = 0.01)
```

```{r, echo=F,warning=F,message=F}
Difference20<-subset(BindingAssays,Parasite== 'IT4var20') %>%
  group_by(DateBinding) %>%
 mutate("Difference" = Count/mean(Count[Genotype=='AA'&Receptor=="EPCR"&Concentration==10])*100)

Difference3d7<-subset(BindingAssays,Parasite== '3d7') %>%
  group_by(DateBinding) %>%
 mutate("Difference" = Count/mean(Count[Genotype=='AA'&Receptor=="CD36"&Concentration==10])*100)

Difference30<-subset(BindingAssays,Parasite== 'IT4var30') %>%
  group_by() %>%
   mutate("Difference" = Count/mean(Count[Genotype=='AA'&Receptor=="CD36"&Concentration==10])*100)
```

# Plots with logistical regression added
```{r, echo=F,warning=F,message=F, fig.width=2.3, fig.height=2}
#3d7
datamodelAA<-subset(Difference3d7,Difference30$Receptor!="EPCR"&Genotype=="AA")
datamodelAS<-subset(Difference3d7,Difference30$Receptor!="EPCR"&Genotype=="AS")
plotdata<-Difference3d7
plotdata$Receptor[plotdata$Receptor=="Control"]<-plotdata$Receptor[plotdata$Receptor=="CD36"]


modelAA <- drm(Difference~Concentration, 
              fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),data=datamodelAA)
modelAS <- drm(Difference~Concentration, 
              fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),data=datamodelAS)
var3d7modelAA<-modelAA
var3d7modelAS<-modelAS

pred.fits <- expand.grid(conc=seq(0.1,11,length=100))
pm<-predict(modelAA,newdata=pred.fits,interval = "confidence")
    pred.fits$p <- pm[,1]
    pred.fits$pmin <- pm[,2]
    pred.fits$pmax <- pm[,3]
pred.fits_1 <- data.frame(Genotype = "AA", pred.fits) 

pm<-predict(modelAS,newdata=pred.fits,interval = "confidence")
    pred.fits$p <- pm[,1]
    pred.fits$pmin <- pm[,2]
    pred.fits$pmax <- pm[,3]
pred.fits_2 <- data.frame(Genotype = "AS", pred.fits)
pred<-rbind(pred.fits_1,pred.fits_2)

p4<-ggplot(plotdata,aes(x=(Concentration),y=Difference,color=Genotype,alpha=0.9))+
  geom_point(aes(shape=(Receptor)))+
  xlab("Protein spot (µg/ml) ")+
  ylab("Relative binding (%)")+
  theme_bw() +
  coord_cartesian(ylim = c(0, 190),xlim=c(0,11))+ scale_y_continuous(breaks = seq(0,180, by=25))+ scale_x_continuous(breaks=c(0,2.5,5,7.5,10))+
  scale_alpha(guide=F)+
  scale_shape_manual(name="Receptor",values = c(16,4))+
  scale_color_manual(values=c("#C84E00", "#339898"))+
  guides(color = guide_legend(order=1),
         shape = guide_legend(order=2,reverse=F))+
  theme(legend.box="vertical", legend.margin=margin(.01,.01,.01,0.01,"cm"),legend.box.margin=margin(0.01),legend.spacing.y = unit(.01, 'cm'),legend.spacing.x = unit(.001, 'cm'),legend.title=element_text(size=8),legend.text = element_text(size=8))

p4 +
  geom_line(data=pred, aes(x=conc, y=p,color=Genotype),size=1)
```

```{r, echo=F,warning=F,message=F, fig.width=2.3, fig.height=2}
datamodelAA<-subset(Difference30,Difference30$Receptor!="EPCR"&Genotype=="AA")
datamodelAS<-subset(Difference30,Difference30$Receptor!="EPCR"&Genotype=="AS")
plotdata<-Difference30
plotdata$Receptor[plotdata$Receptor=="Control"]<-plotdata$Receptor[plotdata$Receptor=="CD36"]

modelAA <- drm(Difference~Concentration, 
              fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),data=datamodelAA)
modelAS <- drm(Difference~Concentration, 
              fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),data=datamodelAS)

var30modelAA<-modelAA
var30modelAS<-modelAS


pred.fits <- expand.grid(conc=seq(0.1,12,length=100))
pm<-predict(modelAA,newdata=pred.fits,interval = "confidence")
    pred.fits$p <- pm[,1]
    pred.fits$pmin <- pm[,2]
    pred.fits$pmax <- pm[,3]
pred.fits_1 <- data.frame(Genotype = "AA", pred.fits) 

pm<-predict(modelAS,newdata=pred.fits,interval = "confidence")
    pred.fits$p <- pm[,1]
    pred.fits$pmin <- pm[,2]
    pred.fits$pmax <- pm[,3]
pred.fits_2 <- data.frame(Genotype = "AS", pred.fits)
pred<-rbind(pred.fits_1,pred.fits_2)

p5<-ggplot(plotdata,aes(x=(Concentration),y=Difference,color=Genotype,alpha=0.9))+
  geom_point(aes(shape=(Receptor)))+
  xlab("Protein spot (µg/ml) ")+
  ylab("Relative binding (%)")+
  theme_bw() +
  coord_cartesian(ylim = c(0, 190),xlim=c(0,11))+ scale_y_continuous(breaks = seq(0,180, by=25))+ scale_x_continuous(breaks=c(0,2.5,5,7.5,10))+
  scale_alpha(guide=F)+
  scale_shape_manual(name="Receptor",values = c(16,4))+
  scale_color_manual(values=c("#C84E00", "#339898"))+
  guides(color = guide_legend(order=1),
         shape = guide_legend(order=2,reverse=F))+
 theme(legend.box="vertical", legend.margin=margin(.01,.01,.01,0,"cm"),legend.box.margin=margin(0.01),legend.spacing.y = unit(.01, 'cm'),legend.spacing.x = unit(.001, 'cm'),legend.title=element_text(size=8),legend.text = element_text(size=8))

p5+
  geom_line(data=pred, aes(x=conc, y=p,color=Genotype),size=1)
```

```{r, echo=F,warning=F,message=F, fig.width=2.3, fig.height=2}
datamodelAA<-subset(Difference20,Difference20$Receptor!="CD36"&Genotype=="AA")
datamodelAS<-subset(Difference20,Difference20$Receptor!="CD36"&Genotype=="AS")

plotdata<-Difference20
plotdata$Receptor[plotdata$Receptor=="Control"]<-plotdata$Receptor[plotdata$Receptor=="EPCR"]
plotdata_summary <- plotdata %>% # the names of the new data frame and the data frame to be summarised
  group_by(Receptor,Genotype,Concentration) %>%   # the grouping variable
  summarise(mean_difference = mean(Difference),  # calculates the mean of each group
            sd_difference = sd(Difference), # calculates the standard deviation of each group
            n_difference = n(),  # calculates the sample size per group
            SE_difference = sd(Difference)/sqrt(n())) # calculates the standard error of each group


modelAA <- drm(Difference~Concentration, 
              fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),data=datamodelAA)
modelAS <- drm(Difference~Concentration, 
              fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),data=datamodelAS)
var20modelAA<-modelAA
var20modelAS<-modelAS

pred.fits <- expand.grid(conc=seq(0.1,10,length=1000))
pm<-predict(modelAA,newdata=pred.fits,interval = "confidence")
    pred.fits$p <- pm[,1]
    pred.fits$pmin <- pm[,2]
    pred.fits$pmax <- pm[,3]
pred.fits_1 <- data.frame(Genotype = "AA", pred.fits) 

pm<-predict(modelAS,newdata=pred.fits,interval = "confidence")
    pred.fits$p <- pm[,1]
    pred.fits$pmin <- pm[,2]
    pred.fits$pmax <- pm[,3]
pred.fits_2 <- data.frame(Genotype = "AS", pred.fits)
pred<-rbind(pred.fits_1,pred.fits_2)

p6<-ggplot(plotdata,aes(x=(Concentration),color=Genotype,alpha=0.9))+
  geom_point(aes(shape=Receptor,y=Difference))+
  xlab("Protein spot (µg/ml) ")+
  ylab("Relative binding (%)")+
  theme_bw() +
  coord_cartesian(ylim = c(0, 190),xlim=c(0,11))+ scale_y_continuous(breaks = seq(0,180, by=25))+ scale_x_continuous(breaks=c(0,2.5,5,7.5,10))+
  scale_alpha(guide=F)+
  scale_shape_manual(name="Receptor",values = c(4,16))+
  scale_color_manual(values=c("#C84E00", "#339898"))+
  guides(color = guide_legend(order=1),
         shape = guide_legend(order=2,reverse=T))+
 theme(legend.box="vertical", legend.margin=margin(.01,.01,.01,0,"cm"),legend.box.margin=margin(0.01),legend.spacing.y = unit(.01, 'cm'),legend.spacing.x = unit(.001, 'cm'),legend.title=element_text(size=8),legend.text = element_text(size=8))

p6+geom_line(data=pred, aes(x=conc, y=p,color=Genotype),size=1)
```

```{r}
#3d7AA
print("3D7 model AA")
summary(var3d7modelAA)
#3d7AS
print("3D7 model AS")
summary(var3d7modelAS)

```

```{r}
#IT4var30AA
print("IT4var30 model AA")
summary(var30modelAA)
#IT4var30AS
print("IT4var30 model AS")
summary(var30modelAS)
```

```{r}
#IT4var20AA
print("IT4var20 model AA")
summary(var20modelAA)
#IT4var20AS
print("IT4var20 model AS")
summary(var20modelAS)
```